### 2015-03-02 fundamentals/impl.tex
cleanup

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/framework}
\end{center}
\caption{The \Cyclus core provides \gls{API}s that abstract away the details in
the kernel and allow the archetypes to be loaded into the simulation in a modular
fashion.}
\label{fig:framework}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/agent_uml}
\end{center}
\caption{The inheritance in \Cyclus classes, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstract away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

>>>>

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\textwidth]{./images/framework}
\end{center}
\caption{The \Cyclus core provides \glspl{API} that abstract away the details in
the kernel and allow the archetypes to be loaded into the simulation in a modular
fashion.}
\label{fig:framework}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}
